### 2018-07-12 Testing.Rmd
Created testing notebook, started unifying igraph clustering framework with clique percolation

---
output:
  html_document: default
  pdf_document: default
---
# Basic Network Analysis of Wordbank Data

## Build Networks

List of libraries
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(boot) # functions for bootstrapping
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(directlabels) # direct labeling of data in plots
library(stringr) # common string operations
library(lmtest) #  diagnostic checking in linear regression models
library(rwebppl) # interface to probabilistic programming language WebPPL
library(jsonlite) # JSON parser
library(nlme) # gaussian linear and nonlinear mixed-effects models
library(feather) # read and write fast lightweight binary columnar data
library(broom) # converts R function outputs to tidy data frames
library(HDInterval) # calculate highest density intervals of objects w/ pdf
library(BBmisc) # misc helper functions
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(doParallel)
library(networkD3)
```

@@

vocab <- make_vocab_dataframe(lang="English (American)",
                              lang_form = "WS",
                              lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() # %>%
  # distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
```

Build networks
```{r}
assoc_network <- function(vocab, max_age) {
  vocab_up_to_age = filter(vocab, age <= max_age)
  assoc_links <- make_assoc_pairs(lemma_list = vocab_up_to_age) %>%
    filter(link==1) %>%
    select(item, pair, item.definition, pair.definition)
  graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=vocab_up_to_age) %>%
    simplify() %>%
    set.graph.attribute("name", "Assoc") %>%
    set.graph.attribute("age", max_age)
  return(graph)
}

@@

```{r, results='asis'}
network_properties <- function(networks) {
  return( tibble(
  names = map_chr(networks, ~ .x$name),
  ages = map_dbl(networks, ~ .x$age) %>%
    as.integer(),
  vertices = map_int(networks, vcount),
  edges = map_dbl(networks, ecount) %>%
    as.integer(), # for some reason igraph ecount returns double
  avg_degree = map(networks, degree) %>%
    map_dbl(mean),
  avg_shortest_path = map_dbl(networks, mean_distance),
  diameter = map_dbl(networks, diameter) %>%
    as.integer(),
  clustering_coefficient = map_dbl(networks, transitivity),
  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
  diameter_random = 0,
  clustering_coefficient_random = 0) )
}

@@

plot(g,vertex.size=.01,vertex.label.cex=.8,
     layout=layout.fruchterman.reingold(g, niter=10000, 
                                        area=40*vcount(g)^2),
     edge.width=E(g)$weight)
```

Test Clique Percolation
```{r}
### Register Parallelisation (used by clique.community.opt.par())
cl <- makeCluster(4)
registerDoParallel(cl)
getDoParWorkers()

@@

#which one? the outcome is always the same
res <- res3

@@

Initial Clique Analysis
```{r}
age <- 20
g <- assoc_networks[[age - 15]]
g <- delete.vertices(g, degree(g)==0)
res <- clique.community.opt(g,3)

>>>>

---
output:
  html_document: default
  pdf_document: default
---
# Testing of Functions and Techniques for Graph Analysis and Display

List of libraries
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(boot) # functions for bootstrapping
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(directlabels) # direct labeling of data in plots
library(stringr) #common string operations
library(lmtest) #  diagnostic checking in linear regression models
library(rwebppl) # interface to probabilistic programming language WebPPL
library(jsonlite) # JSON parser
library(nlme) # gaussian linear and nonlinear mixed-effects models
library(feather) # read and write fast lightweight binary columnar data
library(broom) # converts R function outputs to tidy data frames
library(HDInterval) # calculate highest density intervals of objects w/ pdf
library(BBmisc) # misc helper functions
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(doParallel)
library(networkD3)
```

@@

vocab <- make_vocab_dataframe(lang="English (American)",
                              lang_form = "WS",
                              lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() %>%
  distinct(uni_lemma, .keep_all = TRUE) # remove words with the same uni_lemma?
```

Build networks
```{r, warning = FALSE }
assoc_network <- function(vocab, max_age) {
  vocab_up_to_age = filter(vocab, age <= max_age)
  assoc_links <- make_assoc_pairs(lemma_list = vocab_up_to_age) %>%
    filter(link==1) %>%
    select(item, pair, item.definition, pair.definition)
  graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=vocab_up_to_age) %>%
    simplify() %>%
    set.graph.attribute("name", "Assoc") %>%
    set.graph.attribute("age", max_age)
  return(graph)
}

@@

```{r, results='asis'}
network_properties <- function(networks) {
  return( tibble(
  names = map_chr(networks, ~ .x$name),
  ages = map_dbl(networks, ~ .x$age) %>%
    as.integer(),
  vertices = map_int(networks, vcount),
  edges = map_dbl(networks, ecount) %>%
    as.integer(), # for some reason igraph ecount returns double
  avg_degree = map(networks, degree) %>%
    map_dbl(mean),
  avg_shortest_path = map_dbl(networks, mean_distance),
  diameter = map_dbl(networks, diameter) %>%
    as.integer(),
  clustering_coefficient = map_dbl(networks, transitivity),
  p_random = edges / (vertices * (vertices - 1) / 2),
  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
  diameter_random = 0,
  clustering_coefficient_random = p_random ) )
}

@@

plot(g, vertex.label=V(g)$uni_lemma, vertex.size=.01,vertex.label.cex=.8,
     layout=layout.fruchterman.reingold(g, niter=10000, 
                                        area=40*vcount(g)^2),
     edge.width=E(g)$weight)
```

Test Clique Percolation
```{r}
## Register Parallelisation (used by clique.community.opt.par())
cl <- makeCluster(4)
registerDoParallel(cl)
getDoParWorkers()

@@

#which one? the outcome is always the same
res <- res2

@@

Initial Clique Analysis
```{r}
age <- 20
g <- feature_networks[[age - 15]]
g <- delete.vertices(g, degree(g)==0)
res <- clique.community.opt(g,3)
